SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2018-07-25 scipy-1.0/paper.tex
Add section on API/ABI evolution.

\subsection*{API and ABI evolution}
In general, we encourage changes that improve clarity in the API of the library,
but strongly discourage breaking backwards compatibility, given our position near
the base of the scientific Python computing stack.

>>>>

\subsection*{API and ABI evolution}
The application programming interface (API) for SciPy consists of
approximately 2600 functions and classes. Adding new functionality has to
meet the following criteria:
\begin{itemize}
    \item The algorithm is of relevance to multiple fields of science.
    \item The implementation is demonstrably important.  E.g., it is classic
    enough to be included in textbooks, or it is based on a peer-reviewed article
    which has a significant number of citations.
\end{itemize}

Our policy for evolving the API over time is that new functionality can be added,
while removing or changing existing functionality can only be done if the benefits
of that exceeds the (often significant) costs to users, \textit{and} only
after giving clear deprecation warnings to those users for at least one year.
In general, we encourage changes that improve clarity in the API of the
library but strongly discourage breaking backwards compatibility\footnote{
    Backwards compatibility means that new versions of SciPy will keep user
    code written for an older version working.}
given our position near the base of the scientific Python computing stack.

In addition to the Python API, SciPy has C and Cython interfaces in a number
of submodules. Therefore, we have to also consider the application binary
interface (ABI). This ABI has been stable for a long time, and we aim to
evolve it only in a backwards compatible way.
